Non-word repetition in Yélî Dnye

### 2020-05-20 manuscript.Rmd
updated todo

- add ana based on phonemes & expand on levenshtein
- add ana based on number of characters
- add summary of types of error: %semantic, %deletion (which sounds?) %subst (which are the most common sounds) 
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
- add analysis on the basis of demo chars
- discussion

@@

```{r exclude subsequent}
trnsc=trnsc[trnsc$attempt=="first",]
```

>>>>

- add table r/d by stim length & age
- add table with stimuli
- ask Middy about consent, correct, accuracy
- double check demo: exact age missing: 78, 82, 83, 115, 119; rough age missing 78, there's a mixture of BGMF in sex, first born is missing, round age
- 
- add ana based on phonemes & expand on levenshtein
- add ana based on number of characters
- add summary of types of error: %semantic, %deletion (which sounds?) %subst (which are the most common sounds) 
- maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
- add analysis on the basis of demo chars
- discussion

@@

```{r exclude subsequent}
trnsc=trnsc[trnsc$attempt=="first",]

aggregate(trnsc$correct*100,by=list(trnsc$id,trnsc$age.exact,trnsc$type),mean)->pwcm_att
colnames(pwcm_att)<-c("ID","Age","Length","Word")

mean(pwcm_att$Word[pwcm_att$Length==2],na.rm=T)
```
